### 2019-04-02 papers/journal/encoding.tex
Key difference in encoding section fixed

\subsubsection{The key difference in the reachability encoding}:
The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using non-determinism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the $\fsmt$ encoding, reachability is encoded in two different
ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of non-reachability.
%
On the other hand, we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1}, which needs relatively more auxiliary variables.
%
This is because constraint~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

>>>>

\subsubsection{The key difference in the reachability encoding}:
The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using non-determinism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the $\fsmt$ encoding, reachability is encoded in two different
ways in constraints $\texttt{Paths}(r)$ and $\texttt{FReach}(d,r')$.
%
The reachability is recursively defined in~$\texttt{FReach}(d,r')$ and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
only the solutions that captures the evidence of non-reachability.
%
On the other hand, we have added length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
%
This is because constraint~$\texttt{Loop}(r)$ has only positive
occurrences of the reachability variables and if we had defined
$r$s in~$\texttt{Paths}(r)$ without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

### 2019-04-02 papers/journal/property.tex
Key difference in encoding section fixed

\todo{This section needs a revision}
We analyze the model against our desired properties.
%
\ankit{Not completely correct}Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be true in all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.

% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:

\begin{enumerate}
\item {\em Existential condition:}
if there is a VTS that satisfies the connectedness property.

\item {\em Universal condition:}
  if there is a connectedness property that is satisfied by each valid VTS.
\end{enumerate}

The goal is to find the minimum graph connectivity properties for each of the condition.

% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions.

\subsubsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%
% Used E as edge and L_e L_n as label for node and the edge,

>>>>

We analyze the model against our desired properties.
%
\ankit{Not completely correct}Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be true in all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.
% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:
\begin{enumerate}
\item {\em Existential condition:}
if there is a VTS that satisfies the connectedness property.

\item {\em Universal condition:}
  if there is a connectedness property that is satisfied by each valid VTS.
\end{enumerate}
The goal is to find the minimum graph connectivity properties for each of the condition.
% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions. 
\subsubsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%
% Used E as edge and L_e L_n as label for node and the edge,
